An umbrella review of the benefits and risks associated with youths' interactions with electronic screens

### 2023-06-19 reports/manuscript.tex
Rerun pipeline

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={An umbrella review of the benefits and risks associated with youths' interactions with electronic screens},
  pdfauthor={Taren Sanders*1, Michael Noetel2, Philip Parker1, Borja Del Pozo Cruz3, Stuart Biddle4, 13, Rimante Ronto5, Ryan Hulteen6, Rhiannon Parker7, George Thomas8, Katrien De Cocker9, Jo Salmon10, Kylie Hesketh10, Nicole Weeks1, Hugh Arnott1, Emma Devine11, Roberta Vasconcellos1, Rebecca Pagano12, Jamie Sherson12, James Conigrave1, \& Chris Lonsdale1},
  pdflang={en-EN},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\linenumbers
\usepackage{csquotes}
\usepackage{makecell}
\usepackage{booktabs}
\usepackage{colortbl}
\ifxetex
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[shorthands=off,main=english]{babel}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newenvironment{cslreferences}%
  {}%
  {\par}

\title{An umbrella review of the benefits and risks associated with youths' interactions with electronic screens}
\author{Taren Sanders*\textsuperscript{1}, Michael Noetel\textsuperscript{2}, Philip Parker\textsuperscript{1}, Borja Del Pozo Cruz\textsuperscript{3}, Stuart Biddle\textsuperscript{4, 13}, Rimante Ronto\textsuperscript{5}, Ryan Hulteen\textsuperscript{6}, Rhiannon Parker\textsuperscript{7}, George Thomas\textsuperscript{8}, Katrien De Cocker\textsuperscript{9}, Jo Salmon\textsuperscript{10}, Kylie Hesketh\textsuperscript{10}, Nicole Weeks\textsuperscript{1}, Hugh Arnott\textsuperscript{1}, Emma Devine\textsuperscript{11}, Roberta Vasconcellos\textsuperscript{1}, Rebecca Pagano\textsuperscript{12}, Jamie Sherson\textsuperscript{12}, James Conigrave\textsuperscript{1}, \& Chris Lonsdale\textsuperscript{1}}
\date{}

@@

\affiliation{\vspace{0.5cm}\textsuperscript{1} Institute for Positive Psychology and Education, Australian Catholic University, North Sydney, Australia\\\textsuperscript{2} School of Psychology, University of Queensland, Brisbane, Australia\\\textsuperscript{3} Department of Sport Science and Clinical Biomechanics, University of Southern Denmark, Odense, Denmark\\\textsuperscript{4} Centre for Health Research, University of Southern Queensland, Springfield, Australia\\\textsuperscript{5} Department of Health Sciences, Faculty of Medicine, Health and Human Sciences, Macquarie University, Macquarie Park, Australia\\\textsuperscript{6} School of Kinesiology, Louisiana State University, Baton Rouge, USA\\\textsuperscript{7} The Centre for Social Impact, University of New South Wales, Sydney, Australia\\\textsuperscript{8} The University of Queensland, Health and Wellbeing Centre for Research Innovation, School of Human Movement and Nutrition Sciences, Brisbane, Australia\\\textsuperscript{9} Department of Movement and Sport Science, Ghent University, Ghent, Belgium\\\textsuperscript{10} Institute for Physical Activity and Nutrition, Deakin University, Geelong, Australia\\\textsuperscript{11} The Matilda Centre for Research in Mental Health and Substance Use, University of Sydney, Sydney, Australia\\\textsuperscript{12} School of Education, Australian Catholic University, North Sydney, Australia\\\textsuperscript{13} Faculty of Sport \& Health Sciences, University of Jyväskylä, Finland}

@@

In 2016, the American Academy of Pediatrics used a narrative review to examine the benefits and risks of children and adolescents' electronic media\textsuperscript{20} as a basis for updating their guidelines about screen use.\textsuperscript{15}
Since then, a large number of systematic reviews and meta-analyses have provided evidence about the potential benefits and risks of screen use.
While there have been other overviews of reviews on screen use, these have tended to focus on a single domain (e.g., health\textsuperscript{21}), focus on a particular exposure (e.g., social media\textsuperscript{22,23}) or provide only a narrative summary of the literature.\textsuperscript{24}
Focusing on a single domain or exposure makes it difficult to understand what trade-offs are involved in any guidelines around screen use.
For example, prohibiting screen use might reduce exposure to advertising but may also thwart learning opportunities from interactive educational tools.
Reviews on either of these exposures or outcomes would likely miss being able to quantify these trade-offs.
Overviews are one method of evidence synthesis that helps address these trade-offs, by providing `user-friendly' summaries of a field of research.\textsuperscript{25}
These overviews provide a reference point for the field and allow for easier comparison of risks and benefits for the same behaviour.
By analogy, reading is a sedentary behaviour, and only by comparing the health risks against the educational benefits can researchers and policymakers make clear recommendations about what young people should do.

@@

As shown in Figure 2, most of the credible results (14 of 23 effects) showed statistically significant associations, with 99.9\% confidence intervals not encompassing zero (strong evidence).
The remaining six associations were significant at the 95\% confidence level (weak evidence).
All credible effects related to education outcomes were small-to-moderate.
Screen-based interventions designed to influence an outcome (e.g., a computer based program designed to enhance learning\textsuperscript{26}) tended to have larger effect sizes than exposures that were not specifically intended to influence any of the measured outcomes (e.g., the association between television viewing and learning\textsuperscript{27}).
The largest effect size observed was for augmented reality-based education interventions on general learning (\(r = 0.33, k = 15, N = 1,474\)).
Most effects showed high levels of heterogeneity (18 of 23 with \(I^2 > 50\%\)).

@@

Screen use research has a well-established measurement problem, which impacts the individual studies of this umbrella review.
The vast majority of screen use research relies on self-reported data, which not only lacks the nuance required for understanding the effects of screen use, but may also be inaccurate.
In one systematic review on screen use and sleep,\textsuperscript{7} 66 of the 67 included studies used self-reported data for \emph{both} the exposure and outcome variable.
It has been established that self-reported screen use data has questionable validity.
In a meta-analysis of 47 studies comparing self-reported media use with logged measures, Parry et al\textsuperscript{42} found that the measures were only moderately correlated (\(r = 0.38\)), with self-reported problematic usage fairing worse (\(r = 0.25\)).
Indeed, of 622 studies which measured the screen use of 0---6 year-olds, only 69 provided any sort of psychometric properties for their measure, with only 19 studies reporting validity.\textsuperscript{43}
While some researchers have started using newer methods of capturing screen behaviours---such as wearable cameras\textsuperscript{44} or device-based loggers\textsuperscript{45}---these are still not widely adopted.
It may be that the field of screen use research cannot be sufficiently advanced until accurate, validated, and nuanced measures are more widely available and adopted.

@@

Our high-level approach limits the feasibility of examining fine-grained details of the individual studies.
For example, we did not examine moderators beyond age, nor did we rate the risk of bias for the individual studies.
Thus, our assessment of evidence quality was restricted to statistical credibility, rather than a more complete assessment of quality (e.g., GRADE\textsuperscript{46}).
As such, we made decisions regarding the credibility of evidence, where others may have used different thresholds or metrics.
In addition, when faced with duplicate outcome/exposure combinations we chose to keep the one with the largest pooled sample size, assuming that this would capture the most comprehensive and most recent review.
Inspection of the excluded effect sizes suggests that this decision was not that impactful: our results would have been almost exactly the same has we used the number of included studies (\emph{k}) or the most recent review by publication year.
However, we provide the complete results in the supplementary material, along with the dataset for others to consider alternative criteria.

@@

\hypertarget{refs}{}
\begin{cslreferences}
\leavevmode\hypertarget{ref-blairReadingStrategiesCoping2003}{}%
1. Blair, A. Reading Strategies for Coping With Information Overload ca.1550-1700. \emph{Journal of the History of Ideas} \textbf{64}, 11--28 (2003).

\leavevmode\hypertarget{ref-bell1883sanitarian}{}%
2. Bell, A. N. \emph{The sanitarian}. vol. 11 (AN Bell, 1883).

\leavevmode\hypertarget{ref-dill2013oxford}{}%
3. Dill, K. E. \emph{The Oxford handbook of media psychology}. (Oxford University Press, 2013).

\leavevmode\hypertarget{ref-wartellaChildrenComputersNew2000}{}%
4. Wartella, E. A. \& Jennings, N. Children and computers: New technology. Old concerns. \emph{The future of children} 31--43 (2000).

\leavevmode\hypertarget{ref-rhodes2015top}{}%
5. Rhodes, A. \emph{Top ten child health problems: What the public thinks}. (2015).

\leavevmode\hypertarget{ref-thelancetSocialMediaScreen2019}{}%
6. The Lancet. Social media, screen time, and young people's mental health. \emph{The Lancet} \textbf{393}, 611 (2019).

\leavevmode\hypertarget{ref-haleScreenTimeSleep2015}{}%
7. Hale, L. \& Guan, S. Screen time and sleep among school-aged children and adolescents: A systematic literature review. \emph{Sleep Medicine Reviews} \textbf{21}, 50--58 (2015).

\leavevmode\hypertarget{ref-sweetserActivePassiveScreen2012}{}%
8. Sweetser, P., Johnson, D., Ozdowska, A. \& Wyeth, P. Active versus passive screen time for young children. \emph{Australasian Journal of Early Childhood} \textbf{37}, 94--98 (2012).

\leavevmode\hypertarget{ref-liEarlyChildhoodComputer2004}{}%
9. Li, X. \& Atkins, M. S. Early childhood computer experience and cognitive and motor development. \emph{Pediatrics} \textbf{113}, 1715--1722 (2004).

\leavevmode\hypertarget{ref-warburton2017children}{}%
10. Warburton, W. \& Highfield, K. Children and technology in a smart device world. in \emph{Children, Families and Communities} 195--221 (Oxford University Press, 2017).

\leavevmode\hypertarget{ref-naturehumanbehaviourScreenTimeHow2019}{}%
11. Nature Human Behaviour. Screen time: How much is too much? \emph{Nature} \textbf{565}, 265--266 (2019).

\leavevmode\hypertarget{ref-whoGuidelinesPhysicalActivity2019}{}%
12. World Health Organization. \emph{Guidelines on physical activity, sedentary behaviour and sleep for children under 5 years of age}. 33 p. (World Health Organization, 2019).

\leavevmode\hypertarget{ref-australiangovernmentPhysicalActivityExercise2021}{}%
13. Australian Government. \emph{Physical activity and exercise guidelines for all Australians}. (2021).

\leavevmode\hypertarget{ref-Canadian24HourMovement2016}{}%
14. Canadian Society for Exercise Physiology. \emph{Canadian 24-Hour Movement Guidelines for Children and Youth: An Integration of Physical Activity, Sedentary Behaviour, and Sleep}. (2016).

\leavevmode\hypertarget{ref-AAPMediaUseSchoolAged2016}{}%
15. Council On Communication and Media. Media Use in School-Aged Children and Adolescents. \emph{Pediatrics} \textbf{138}, e20162592 (2016).

\leavevmode\hypertarget{ref-fergusonEverythingModerationModerate2017}{}%
16. Ferguson, C. J. Everything in Moderation: Moderate Use of Screens Unassociated with Child Behavior Problems. \emph{Psychiatric Quarterly} \textbf{88}, 797--805 (2017).

\leavevmode\hypertarget{ref-przybylskiLargeScaleTestGoldilocks2017}{}%
17. Przybylski, A. K. \& Weinstein, N. A Large-Scale Test of the Goldilocks Hypothesis: Quantifying the Relations Between Digital-Screen Use and the Mental Well-Being of Adolescents. \emph{Psychological Science} \textbf{28}, 204--215 (2017).

\leavevmode\hypertarget{ref-sandersTypeScreenTime2019}{}%
18. Sanders, T., Parker, P. D., del Pozo-Cruz, B., Noetel, M. \& Lonsdale, C. Type of screen time moderates effects on outcomes in 4013 children: Evidence from the Longitudinal Study of Australian Children. \emph{International Journal of Behavioral Nutrition and Physical Activity} \textbf{16}, 117 (2019).

\leavevmode\hypertarget{ref-kayeConceptualMethodologicalMayhem2020}{}%
19. Kaye, L. K., Orben, A., Ellis, D. A., Hunter, S. C. \& Houghton, S. The Conceptual and Methodological Mayhem of `Screen Time'. \emph{International Journal of Environmental Research and Public Health} \textbf{17}, 3661 (2020).

\leavevmode\hypertarget{ref-chassiakosChildrenAdolescentsDigital2016}{}%
20. Chassiakos, Y. L. R. \emph{et al.} Children and Adolescents and Digital Media. \emph{Pediatrics} \textbf{138}, e20162593 (2016).

\leavevmode\hypertarget{ref-stiglicEffectsScreentimeHealth2019}{}%
21. Stiglic, N. \& Viner, R. M. Effects of screentime on the health and well-being of children and adolescents: A systematic review of reviews. \emph{BMJ Open} \textbf{9}, e023191 (2019).

\leavevmode\hypertarget{ref-valkenburgSocialMediaUse2022}{}%
22. Valkenburg, P. M., Meier, A. \& Beyens, I. Social media use and its impact on adolescent mental health: An umbrella review of the evidence. \emph{Current Opinion in Psychology} \textbf{44}, 58--68 (2022).

\leavevmode\hypertarget{ref-arias-delatorreRelationshipDepressionUse2020}{}%
23. Arias-de la Torre, J. \emph{et al.} Relationship Between Depression and the Use of Mobile Technologies and Social Media Among Adolescents: Umbrella Review. \emph{Journal of Medical Internet Research} \textbf{22}, e16388 (2020).

\leavevmode\hypertarget{ref-orbenTeenagersScreensSocial2020}{}%
24. Orben, A. Teenagers, screens and social media: A narrative review of reviews and key studies. \emph{Social Psychiatry and Psychiatric Epidemiology} \textbf{55}, 407--414 (2020).

\leavevmode\hypertarget{ref-pollockChapterOverviewsReviews2022}{}%
25. Pollock, M., Fernandes, R., Becker, L., Pieper, D. \& Hartling, L. Chapter V: Overviews of Reviews. in \emph{Cochrane Handbook for Systematic Reviews of Interventions} (eds. Higgins, J. P. et al.) (Cochrane, 2022).

\leavevmode\hypertarget{ref-xieCanTouchscreenDevices2018}{}%
26. Xie, H. \emph{et al.} Can Touchscreen Devices be Used to Facilitate Young Children's Learning? A Meta-Analysis of Touchscreen Learning Effect. \emph{Frontiers in Psychology} \textbf{9}, 2580 (2018).

\leavevmode\hypertarget{ref-adelantado-renauAssociationScreenMedia2019}{}%
27. Adelantado-Renau, M. \emph{et al.} Association Between Screen Media Use and Academic Performance Among Children and Adolescents: A Systematic Review and Meta-analysis. \emph{JAMA Pediatrics} \textbf{173}, 1058 (2019).

\leavevmode\hypertarget{ref-madiganAssociationsScreenUse2020}{}%
28. Madigan, S., McArthur, B. A., Anhorn, C., Eirich, R. \& Christakis, D. A. Associations Between Screen Use and Child Language Skills: A Systematic Review and Meta-analysis. \emph{JAMA Pediatrics} \textbf{174}, 665 (2020).

\leavevmode\hypertarget{ref-poorolajalBehavioralFactorsInfluencing2020}{}%
29. Poorolajal, J., Sahraei, F., Mohamdadi, Y., Doosti-Irani, A. \& Moradi, L. Behavioral factors influencing childhood obesity: A systematic review and meta-analysis. \emph{Obesity Research \& Clinical Practice} \textbf{14}, 109--118 (2020).

\leavevmode\hypertarget{ref-byunDigitalGamebasedLearning2018}{}%
30. Byun, J. \& Joung, E. Digital game-based learning for K-12 mathematics education: A meta-analysis. \emph{School Science and Mathematics} \textbf{118}, 113--126 (2018).

\leavevmode\hypertarget{ref-vannucciSocialMediaUse2020}{}%
31. Vannucci, A., Simpson, E. G., Gagnon, S. \& Ohannessian, C. M. Social media use and risky behaviors in adolescents: A meta-analysis. \emph{Journal of Adolescence} \textbf{79}, 258--274 (2020).

\leavevmode\hypertarget{ref-yoonSocialNetworkSite2019}{}%
32. Yoon, S., Kleinman, M., Mertz, J. \& Brannick, M. Is social network site usage related to depression? A meta-analysis of FacebookDepression relations. \emph{Journal of Affective Disorders} \textbf{248}, 65--72 (2019).

\leavevmode\hypertarget{ref-vahediAssociationSelfreportedDepressive2021}{}%
33. Vahedi, Z. \& Zannella, L. The association between self-reported depressive symptoms and the use of social networking sites (SNS): A meta-analysis. \emph{Current Psychology} \textbf{40}, 2174--2189 (2021).

\leavevmode\hypertarget{ref-seetharamanFacebookKnowsInstagram2021}{}%
34. Seetharaman, G. W., Jeff Horwitz and Deepa. Facebook Knows Instagram Is Toxic for Teen Girls, Company Documents Show. \emph{Wall Street Journal} (2021).

\leavevmode\hypertarget{ref-tekedereExaminingEffectivenessAugmented2016}{}%
35. Tekedere, H. \& Göke, H. Examining the Effectiveness of Augmented Reality Applications in Education: A Meta-Analysis. \emph{International Journal of Environmental and Science Education} \textbf{11}, 9469--9481 (2016).

\leavevmode\hypertarget{ref-sadeghiradInfluenceUnhealthyFood2016}{}%
36. Sadeghirad, B., Duhaney, T., Motaghipisheh, S., Campbell, N. R. C. \& Johnston, B. C. Influence of unhealthy food and beverage marketing on children's dietary intake and preference: A systematic review and meta-analysis of randomized trials. \emph{Obesity Reviews} \textbf{17}, 945--959 (2016).

\leavevmode\hypertarget{ref-marshallRelationshipsMediaUse2004}{}%
37. Marshall, S. J., Biddle, S. J. H., Gorely, T., Cameron, N. \& Murdey, I. Relationships between media use, body fatness and physical activity in children and youth: A meta-analysis. \emph{International Journal of Obesity} \textbf{28}, 1238--1246 (2004).

\leavevmode\hypertarget{ref-elsonPolicyStatementsMedia2019}{}%
38. Elson, M. \emph{et al.} Do policy statements on media effects faithfully represent the science? \emph{Advances in Methods and Practices in Psychological Science} \textbf{2}, 12--25 (2019).

\leavevmode\hypertarget{ref-ashtonScreenTimeChildren2019}{}%
39. Ashton, J. J. \& Beattie, R. M. Screen time in children and adolescents: Is there evidence to guide parents and policy? \emph{The Lancet Child \& Adolescent Health} \textbf{3}, 292--294 (2019).

\leavevmode\hypertarget{ref-royalcollegeofpaediatricsandchildhealthHealthImpactsScreen2019}{}%
40. Royal College of Paediatrics and Child Health. \emph{The health impacts of screen time: A guide for clinicians and parents.} (2019).

\leavevmode\hypertarget{ref-pagePRISMA2020Statement2020}{}%
41. Page, M. J. \emph{et al.} \emph{The PRISMA 2020 statement: An updated guideline for reporting systematic reviews}. (2020) doi:\href{https://doi.org/10.31222/osf.io/v7gm2}{10.31222/osf.io/v7gm2}.

\leavevmode\hypertarget{ref-parrySystematicReviewMetaanalysis2021}{}%
42. Parry, D. A. \emph{et al.} A systematic review and meta-analysis of discrepancies between logged and self-reported digital media use. \emph{Nature Human Behaviour} \textbf{5}, 1535--1547 (2021).

\leavevmode\hypertarget{ref-byrneMeasurementScreenTime2021}{}%
43. Byrne, R., Terranova, C. O. \& Trost, S. G. Measurement of screen time among young children aged 0 years: A systematic review. \emph{Obesity Reviews} \textbf{22}, (2021).

\leavevmode\hypertarget{ref-smithFeasibilityAutomatedCameras2019}{}%
44. Smith, C., Galland, B. C., de Bruin, W. E. \& Taylor, R. W. Feasibility of automated cameras to measure screen use in adolescents. \emph{American journal of preventive medicine} \textbf{57}, 417--424 (2019).

\leavevmode\hypertarget{ref-rydingPassiveObjectiveMeasures2020}{}%
45. Ryding, F. C. \& Kuss, D. J. Passive objective measures in the assessment of problematic smartphone use: A systematic review. \emph{Addictive Behaviors Reports} \textbf{11}, 100257 (2020).

\leavevmode\hypertarget{ref-guyattGRADEGuidelinesIntroduction2011}{}%
46. Guyatt, G. \emph{et al.} GRADE guidelines: 1. IntroductionGRADE evidence profiles and summary of findings tables. \emph{Journal of Clinical Epidemiology} \textbf{64}, 383--394 (2011).

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={An umbrella review of the benefits and risks associated with youths' interactions with electronic screens},
  pdfauthor={Taren Sanders*1, Michael Noetel2, Philip Parker1, Borja Del Pozo Cruz3, 14, 15, Stuart Biddle4, 13, Rimante Ronto5, Ryan Hulteen6, Rhiannon Parker7, George Thomas8, Katrien De Cocker9, Jo Salmon10, Kylie Hesketh10, Nicole Weeks1, Hugh Arnott1, Emma Devine11, Roberta Vasconcellos1, Rebecca Pagano12, Jamie Sherson12, James Conigrave1, \& Chris Lonsdale1},
  pdflang={en-EN},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\linenumbers
\usepackage{csquotes}
\usepackage{makecell}
\usepackage{booktabs}
\usepackage{colortbl}
\ifXeTeX
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[main=english]{babel}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
\fi
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\title{An umbrella review of the benefits and risks associated with youths' interactions with electronic screens}
\author{Taren Sanders*\textsuperscript{1}, Michael Noetel\textsuperscript{2}, Philip Parker\textsuperscript{1}, Borja Del Pozo Cruz\textsuperscript{3, 14, 15}, Stuart Biddle\textsuperscript{4, 13}, Rimante Ronto\textsuperscript{5}, Ryan Hulteen\textsuperscript{6}, Rhiannon Parker\textsuperscript{7}, George Thomas\textsuperscript{8}, Katrien De Cocker\textsuperscript{9}, Jo Salmon\textsuperscript{10}, Kylie Hesketh\textsuperscript{10}, Nicole Weeks\textsuperscript{1}, Hugh Arnott\textsuperscript{1}, Emma Devine\textsuperscript{11}, Roberta Vasconcellos\textsuperscript{1}, Rebecca Pagano\textsuperscript{12}, Jamie Sherson\textsuperscript{12}, James Conigrave\textsuperscript{1}, \& Chris Lonsdale\textsuperscript{1}}
\date{}

@@

\affiliation{\vspace{0.5cm}\textsuperscript{1} Institute for Positive Psychology and Education, Australian Catholic University, North Sydney, Australia\\\textsuperscript{2} School of Psychology, University of Queensland, Brisbane, Australia\\\textsuperscript{3} Department of Sport Science and Clinical Biomechanics, University of Southern Denmark, Odense, Denmark\\\textsuperscript{4} Centre for Health Research, University of Southern Queensland, Springfield, Australia\\\textsuperscript{5} Department of Health Sciences, Faculty of Medicine, Health and Human Sciences, Macquarie University, Macquarie Park, Australia\\\textsuperscript{6} School of Kinesiology, Louisiana State University, Baton Rouge, USA\\\textsuperscript{7} The Centre for Social Impact, University of New South Wales, Sydney, Australia\\\textsuperscript{8} The University of Queensland, Health and Wellbeing Centre for Research Innovation, School of Human Movement and Nutrition Sciences, Brisbane, Australia\\\textsuperscript{9} Department of Movement and Sport Science, Ghent University, Ghent, Belgium\\\textsuperscript{10} Institute for Physical Activity and Nutrition, Deakin University, Geelong, Australia\\\textsuperscript{11} The Matilda Centre for Research in Mental Health and Substance Use, University of Sydney, Sydney, Australia\\\textsuperscript{12} School of Education, Australian Catholic University, North Sydney, Australia\\\textsuperscript{13} Faculty of Sport \& Health Sciences, University of Jyväskylä, Finland\\\textsuperscript{14} Department of Physical Education, Faculty of Education, University of Cádiz, Cádiz, Spain\\\textsuperscript{15} Biomedical Research and Innovation Institute of Cádiz (INiBICA) Research Unit, Puerta del Mar University Hospital, University of Cádiz, Cádiz, Spain}

@@

In 2016, the American Academy of Pediatrics used a narrative review to examine the benefits and risks of children and adolescents' electronic media\textsuperscript{20} as a basis for updating their guidelines about screen use.\textsuperscript{15}
Since then, a large number of systematic reviews and meta-analyses have provided evidence about the potential benefits and risks of screen use.
While there have been other overviews of reviews on screen use, these have tended to focus on a single domain (e.g., health),\textsuperscript{21} focus on a particular exposure (e.g., social media)\textsuperscript{22,23} or provide only a narrative summary of the literature.\textsuperscript{24}
Focusing on a single domain or exposure makes it difficult to understand what trade-offs are involved in any guidelines around screen use.
For example, prohibiting screen use might reduce exposure to advertising but may also thwart learning opportunities from interactive educational tools.
Reviews on either of these exposures or outcomes would likely miss being able to quantify these trade-offs.
Overviews are one method of evidence synthesis that helps address these trade-offs, by providing `user-friendly' summaries of a field of research.\textsuperscript{25}
These overviews provide a reference point for the field and allow for easier comparison of risks and benefits for the same behaviour.
By analogy, reading is a sedentary behaviour, and only by comparing the health risks against the educational benefits can researchers and policymakers make clear recommendations about what young people should do.

@@

As shown in Figure 2, most of the credible results (14 of 23 effects) showed statistically significant associations, with 99.9\% confidence intervals not encompassing zero (strong evidence).
The remaining six associations were significant at the 95\% confidence level (weak evidence).
All credible effects related to education outcomes were small-to-moderate.
Screen-based interventions designed to influence an outcome (e.g., a computer based program designed to enhance learning)\textsuperscript{26} tended to have larger effect sizes than exposures that were not specifically intended to influence any of the measured outcomes (e.g., the association between television viewing and learning).\textsuperscript{27}
The largest effect size observed was for augmented reality-based education interventions on general learning (\(r = 0.33, k = 15, N = 1,474\)).
Most effects showed high levels of heterogeneity (18 of 23 with \(I^2 > 50\%\)).

@@

Screen use research has a well-established measurement problem, which impacts the individual studies of this umbrella review.
The vast majority of screen use research relies on self-reported data, which not only lacks the nuance required for understanding the effects of screen use, but may also be inaccurate.
In one systematic review on screen use and sleep,\textsuperscript{7} 66 of the 67 included studies used self-reported data for \emph{both} the exposure and outcome variable.
It has been established that self-reported screen use data has questionable validity.
In a meta-analysis of 47 studies comparing self-reported media use with logged measures, Parry et al\textsuperscript{42} found that the measures were only moderately correlated (\(r = 0.38\)), with self-reported problematic usage fairing worse (\(r = 0.25\)).
Indeed, of 622 studies which measured the screen use of 0---6 year-olds, only 69 provided any sort of psychometric properties for their measure, with only 19 studies reporting validity.\textsuperscript{43}
While some researchers have started using newer methods of capturing screen behaviours---such as wearable cameras\textsuperscript{44} or device-based loggers---\textsuperscript{45}these are still not widely adopted.
It may be that the field of screen use research cannot be sufficiently advanced until accurate, validated, and nuanced measures are more widely available and adopted.

@@

Our high-level approach limits the feasibility of examining fine-grained details of the individual studies.
For example, we did not examine moderators beyond age, nor did we rate the risk of bias for the individual studies.
Thus, our assessment of evidence quality was restricted to statistical credibility, rather than a more complete assessment of quality (e.g., GRADE).\textsuperscript{46}
As such, we made decisions regarding the credibility of evidence, where others may have used different thresholds or metrics.
In addition, when faced with duplicate outcome/exposure combinations we chose to keep the one with the largest pooled sample size, assuming that this would capture the most comprehensive and most recent review.
Inspection of the excluded effect sizes suggests that this decision was not that impactful: our results would have been almost exactly the same has we used the number of included studies (\emph{k}) or the most recent review by publication year.
However, we provide the complete results in the supplementary material, along with the dataset for others to consider alternative criteria.

@@
